Design, Implementation, and Evaluation of Open Power Quality

### 2020-06-24 04-related.tex
Updates to related.

While the OPQ Box has much more limited functionality, it is designed to be manufactured for approximately \$75, which is 10 to 100 times less expensive than most commercial devices, and similar is cost to OpenZMeter. The most important distinguishing feature of OPQ Box is that it is designed to grid-level, not single point monitoring, and thus incorporates features (such as two way communication with the cloud, and subthreshold triggering) that are not present in devices intended for "stand alone" capabilities.

>>>>

While the OPQ Box has much more limited functionality, it is designed to be manufactured for approximately \$75, which is 10 to 100 times less expensive than most commercial devices, and similar is cost to OpenZMeter. The most important distinguishing feature of OPQ Box is that it is designed to grid-level, not single point monitoring, and thus incorporates features (such as two-way communication with the cloud, and subthreshold triggering) that are not present in devices intended for "stand alone" capabilities.
